---
title: "Stats 506, F20, Final Project"
author: "Jialun Li, ljlstudy@umich.edu"
date: "`r format.Date(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
# 79: -------------------------------------------------------------------------
#! We generally don't need to see the code in the results document.
knitr::opts_chunk$set(echo = FALSE)
source("FinalProject.R")
#! Make sure all chunks have a label. This one is labeled 'setup'.
```

# Introduction
  
  Different commercial buildings have different operation times. Moreover, 
  their operation times may vary from buildings to buildings due to multiple 
  reasons (Regulations, geographic conditions, etc.). However, there may exist 
  some common patterns for the operating time in one specific division, or in 
  one specific building types (Office, shopping mall, lodging houses...). 
  Some buildings will possibly have longer operating hours than others in 
  general.
  
  Hence, in my final project, I decided to carry out analysis to answer this 
  question: **For what portion of the day are different types of commercial ** 
  **buildings typically in use?**
  
  This analysis may be helpful for further energy consumption analysis. For
  example, buildings in longer operation time may have more energy consumed. 
  This analysis will point out which type of commercial buildings in which 
  are in heavily operation each day.
  
  I will analyze *the mean working hours* for buildings in each division with
  different building activities. Moreover, considering that the square
  footage of buildings may have some influence on the final result, besides 
  the per-building analysis, I will also do per-square-footage analysis.
  

# Data & Methods

  The data set I planned to use is the 2012 US Commercial Building Energy 
  Consumption Survey (CBECS) data. My data analysis steps is:
  
  i. Clean the data, select variables in interest and assign labels to the 
  categorical variables. I will only use those truly responded observations for 
  my analysis.
  
  i. Compute the mean proportions for working hours per day grouped by division 
  and principal building activities with 95% confidence intervals using 
  replicate weights.

  *(Special Notes on imputed variables: In this survey, some observations *
  *failed to get accurate responses. For these variables, there are additional *
  *variables with the same name plus a prefix "Z" as the identifier, *
  *determining whether these variables are truly responded, estimated or *
  *imputed.)*


# Results


## Per Building Analysis

``` {r building_mean, echo = FALSE, fig.width = 12, fig.align='center', warning = FALSE}
  wh_mean_plot
```


## Per Square-Footage Analysis

``` {r footage_mean, echo = FALSE, fig.width = 12, fig.align='center', warning = FALSE}
  whsq_mean_plot
```


# Conclusion

  It can be seen that lodging buildings has the longest operation hours among 
  all divisions. It operates almost throughout the day. Food selling 
  buildings also have relatively long operating hours. For other buildings, the 
  operation time varies from division to division. Service buildings, health 
  care buildings and offices occupied the smallest proportion of the day in 
  operation.
  
  The per-square-footage analysis gives approximately the same conclusion. 
  However, the proportions of buildings like laboratory and mall-excluded 
  retail buildings have more variations than the per-building analysis.
  
  This analysis only summarized about 2300 observations and they may not be 
  convincing enough. More detailed analysis will help in answering this 
  question more thoroughly.
  
